---
title: "EV"
author: "User"
date: "4/28/2023"
output: html_document
---

```{r setup, include=FALSE}
# Load required libraries
library(dplyr)
library(tidytext)
library(stringr)
library(tidyr)
library(tm)
library(tseries) # for cointegration test
library(ggplot2) # for plotting
library(dplyr)
library(lmtest)
library(quantmod)
library(readr)
library(readxl)
library(arsenal)
library(vars)
library(lmtest)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(RColorBrewer)
library(topicmodels)
library(MASS)
library(data.table)
library(ggplot2)
library(dplyr)
library(reshape2)
library(tidyr)
library(ggpubr)
library(MASS)
library(leaflet)
library(dplyr)
library(maps)
library(ggplot2)
library(ggmap)

```



```{r, include=FALSE}
library(readr)
data <- read_csv("C:/Users/Victor/Desktop/MAO3754.csv")
View(data)
```

1.Multiple scatterplots (or boxplots) for a categorical variable using the for loop, and export them as jpeg files:

```{r}
library(ggplot2)

# Assuming the categorical variable is "category"
unique_categories <- unique(data$category)

for (category in unique_categories) {
  plot_data <- data[data$category == category, ]
  plot <- ggplot(plot_data, aes(x = parameter, y = value)) + 
    geom_point() + 
    ggtitle(paste("Category:", category)) +
    xlab("Parameter") + ylab("Value")
  ggsave(paste("plot_", category, ".jpeg", sep = ""), plot, device = "jpeg")
}


```


```{r, warning=FALSE}

# Define variables
categorical_var <- "region"
plot_var <- "value"

# Create for loop to generate plots for each level of the categorical variable
for(i in unique(data[[categorical_var]])) {
  plot_data <- data %>% filter(.data[[categorical_var]] == i)
  jpeg(filename = paste0(i,".jpeg"), width = 800, height = 600)
  plot <- ggplot(plot_data, aes_string(x = plot_var)) + geom_boxplot() + ggtitle(i)
  print(plot)
  dev.off()
}

plot_data
```



```{r}
# load required packages
library(ggplot2)

# create a list of unique categories in the 'category' column
cat_list <- unique(data$category)

# create a for loop to create scatterplots or boxplots for each category
for (cat in cat_list) {
  # filter data for a specific category
  cat_data <- data[data$category == cat, ]
  
  # create scatterplot or boxplot depending on the parameter
  if (cat_data$parameter[1] == "CO2 emissions") {
    plot <- ggplot(cat_data, aes(x = year, y = value, color = mode)) +
      geom_point(aes(size = powertrain), alpha = 0.7) +
      ggtitle(paste0(cat, " ", cat_data$parameter[1])) +
      theme_bw()
  } else {
    plot <- ggplot(cat_data, aes(x = mode, y = value, fill = powertrain)) +
      geom_boxplot() +
      ggtitle(paste0(cat, " ", cat_data$parameter[1])) +
      theme_bw()
  }
  
  # save plot as jpeg file
  ggsave(paste0(cat, "_", cat_data$parameter[1], ".jpeg"), plot)
}


```



2. Different types of plots, including scatterplots, boxplots (try to change x axis names and rotate the names to a certain angle), barplots (ideally with standard deviation bar), and pie charts:

```{r}

library(ggplot2)

# Scatterplot
ggplot(data, aes(x = parameter, y = value, color = region)) + 
  geom_point() +
  xlab("Parameter") + ylab("Value") +
  ggtitle("Scatterplot by Region")

# Boxplot with rotated x-axis labels
ggplot(data, aes(x = parameter, y = value, fill = region)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Parameter") + ylab("Value") +
  ggtitle("Boxplot by Region")

# Barplot with standard deviation error bars
library(dplyr)
data_summary <- data %>%
  group_by(region, category, parameter) %>%
  summarize(mean_value = mean(value), sd_value = sd(value))

ggplot(data_summary, aes(x = parameter, y = mean_value, fill = region)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = mean_value - sd_value, ymax = mean_value + sd_value),
                position = position_dodge(0.9), width = 0.25) +
  xlab("Parameter") + ylab("Mean Value") +
  ggtitle("Barplot with Standard Deviation Error Bars by Region")

# Pie chart
library(tidyr)
data_summary2 <- data %>%
  group_by(region) %>%
  summarize(count = n())

ggplot(data_summary2, aes(x = "", y = count, fill = region)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  ggtitle("Pie Chart by Region")

```
3. High-dimension plots using the lattice package, and practice using the tidyr and dplyr packages to do variable selection and wide-to-long table conversion, if your dataset allows to do the conversion:
```{r}
library(ggplot2)

# Convert data to wide format
data_wide <- data %>%
  pivot_wider(names_from = "parameter", values_from = "value")

# Create heatmap using ggplot2
ggplot(data_wide, aes(x = category, y = region, fill = year)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "green", high = "blue") +
  labs(x = "Category", y = "Region", title = "Distribution of New Energy by Region and Category")


```


```{r, error=FALSE, warning=FALSE}
library(lattice)
library(dplyr)

mydata_select <- data %>%
  dplyr::select(category, parameter, mode, powertrain, year, unit, value)

mydata_long <- mydata_select %>%
  gather(key = "variable", value = "value", -category, -parameter, -mode, -powertrain, -year, -unit, -value)

bwplot(value ~ unit | category, data = mydata_long)

stripplot(value ~ unit | category, data = mydata_long, jitter.data = TRUE)


```

4.	applying the qplot() function in ggplot2 to generate scatterplot, boxplot, histogram, line plot, etc. Try to vary color, shape, and size, whenever possible.

```{r, warning=FALSE}
# Scatterplot
qplot(x = value, y = year, data = data, color = region, size = powertrain)

# Boxplot
qplot(x = category, y = value, data = data, geom = "boxplot", color = region)

# Histogram
qplot(x = value, data = data, fill = region, alpha = I(0.5), binwidth = 5)

# Line plot
qplot(x = year, y = value, data = data, group = region, color = region, geom = "line")



```





```{r}

library(ggplot2)

qplot(year, value, data = data, color = region, size = powertrain, alpha = 0.5)

```


```{r}

qplot(region, value, data = data, geom = "boxplot", fill = powertrain)

```


```{r}

qplot(value, data = data, geom = "histogram", binwidth = 100, fill = powertrain, alpha = 0.5)

```

5.	applying the ggplot() function to generate scatterplot, boxplot, histogram, etc. If your dataset allows you to do linear regression, please give it a try, and check the residual trend by generating a plot. In addition, use ggsave() to save figures in png, tiff, and pdf formats.

```{r}
library(ggplot2)

# Scatterplot
ggplot(data = data, aes(x = year, y = value, color = region)) + 
  geom_point(size = 2) +
  ggtitle("Electric Vehicle Sales by Region") +
  xlab("Year") + 
  ylab("Sales") +
  theme_bw()

# Boxplot
ggplot(data = data, aes(x = region, y = value, fill = powertrain)) + 
  geom_boxplot() +
  ggtitle("Electric Vehicle Sales by Region and Powertrain Type") +
  xlab("Region") + 
  ylab("Sales") +
  theme_bw()

# Histogram
ggplot(data = data, aes(x = value)) + 
  geom_histogram(bins = 10, fill = "#0072B2", alpha = 0.5) +
  ggtitle("Electric Vehicle Sales Distribution") +
  xlab("Sales") + 
  ylab("Frequency") +
  theme_bw()

# Linear regression and residual plot
ggplot(data = data, aes(x = year, y = value)) + 
  geom_point(size = 2) +
  ggtitle("Electric Vehicle Sales by Year") +
  xlab("Year") + 
  ylab("Sales") +
  theme_bw() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  ggtitle("Electric Vehicle Sales by Year with Linear Regression") +
  xlab("Year") + 
  ylab("Sales") +
  theme_bw()

# Residual plot
model <- lm(value ~ year, data = data)
ggplot(data = data, aes(x = fitted(model), y = resid(model))) +
  geom_point(alpha = 0.5) +
  ggtitle("Residual Plot") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_bw()



```

6.	different strategies to visualize distributions in 1d and 2d (as a way to deal with overplotting). Try to vary the transparency level and use the jitter() function to reduce overplotting.

```{r}
# 1D density plot with transparency
ggplot(data = data, aes(x = value)) + 
  geom_density(alpha = 0.5, fill = "blue") +
  ggtitle("Electric Vehicle Sales Distribution") +
  xlab("Sales") + 
  ylab("Density") +
  theme_bw()

# 2D scatterplot with jitter and transparency
ggplot(data = data, aes(x = year, y = value)) + 
  geom_jitter(width = 0.1, height = 0, alpha = 0.5) +
  ggtitle("Electric Vehicle Sales by Year") +
  xlab("Year") + 
  ylab("Sales") +
  theme_bw()


```

7. Changing color scales, faceting, and creating contingency table with chi-square test of independence:
```{r}
# Discrete color scale
ggplot(data = data, aes(x = year, y = value, color = powertrain)) + 
  geom_point(size = 2) +
  ggtitle("Electric Vehicle Sales by Powertrain Type") +
  xlab("Year") + 
  ylab("Sales") +
  scale_color_discrete(name = "Powertrain") +
  theme_bw()



```


```{r}

# Create a contingency table
cont_table <- table(data$region, data$category)
cont_table

```


```{r, warning=FALSE}
# Conduct chi-square test of independence
chisq.test(cont_table)


```
8.	applying linear models to explore the relationships between a response variable and multiple independent variables. Try to add a high-order predictor, or try to add an interaction factor between two variables. Visualize your model predictions, and use anova() to compare model performance. Use ggplot() methods to plot residuals from your model.

```{r}
# Fit linear model
model <- lm(value ~ year + mode*powertrain, data = data)

# Print model summary
summary(model)

# Add interaction term
model2 <- lm(value ~ year + mode*powertrain + year*mode, data = data)

# Print model summary
summary(model2)

anova

```


```{r}

# Create scatterplot
ggplot(data = data, aes(x = year, y = value, color = mode)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

```

```{r}

# Load ggfortify package
library(ggfortify)

# Plot residuals
autoplot(model, which = 1)

```


```{r}
# fit linear model
model <- lm(value ~ year * powertrain, data = data)

# print model summary
summary(model)


```


```{r}
# plot model predictions
ggplot(data, aes(x = year, y = value, color = powertrain)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, aes(group = powertrain))


```


```{r}
# plot residuals
ggplot(data = data.frame(x = model$fitted.values, y = model$residuals)) +
  geom_point(aes(x, y))


```


```{r}
# fit simpler model without interaction term
simple_model <- lm(value ~ year + powertrain, data = data)

# compare model performance
anova(simple_model, model)


```




A map showing the distribution of different New energies throughout the world 
```{r}

# Summarize data by region and parameter
summary_data <- aggregate(value ~ region + parameter, data, sum)

# Rename the value column to total_energy
names(summary_data)[names(summary_data)=="value"] <- "total_energy"


```


```{r, warning=FALSE, error=FALSE}
# Get world map data
world_map <- map_data("world")

# Merge map data with summarized data
map_data <- merge(world_map, summary_data, by.x = "region", by.y = "region")

# Create map plot using ggplot2
ggplot() +
  geom_map(data = map_data, map = map_data,
           aes(x = long, y = lat, map_id = region, fill = total_energy),
           color = "pink", size = 0.1) +
  scale_fill_gradient(low = "green", high = "blue") +
  theme_void()


```


```{r}
# Convert data to long format
data_long <- data %>% 
  pivot_longer(cols = c("value"), names_to = "measurement", values_to = "measurement_value")

# Select variables for plotting
plot_data <- data_long %>% 
  dplyr::select(category, parameter, measurement, measurement_value)

# Create high-dimension plot using lattice
xyplot(measurement_value ~ parameter | category * measurement, data = plot_data, 
       type = c("p", "l"), auto.key = TRUE, col = c("yellow", "blue", "grey", "purple"),
       ylim = c(0, 500), xlim = c(0, 500))


```







```{r}


```








